On Secure Delegation of SampBQP with a Classical Client

### 2020-01-21 preliminaries.tex
Make some progress on QPIP0 protocol

Lastly, we recall the definition of a verifiable quantum FHE scheme:
\begin{dfn}
	TODO
\end{dfn}

>>>>

Lastly, we generalize the above security definition to interactive schemes.

\begin{dfn}
	Let $(\bbP, \bbV)(x)$ be an interactive protocol with the verifier's initial input being $x$. Then it is IND-CPA secure if, for any $x_1, x_2$, any polynomial time adversary $\cA$,
	$$\abs{\Pr\left[TODO\right]}-TODO$$

\end{dfn}

### 2020-01-21 privacy.tex
Make some progress on QPIP0 protocol

@@

\floatname{algorithm}{Protocol}
\begin{algorithm}
	\caption{Verifiable, secure, and constant round delegation}
	\label{ProtoPrivateDelegation}
	\begin{algorithmic}[1]
		\Procedure{Delegation}{C, x}
			\State $\mathsf{QHE.Keygen}\rightarrow(pk, evk, sk)$
			\State Let $\tilde{x}=\mathsf{Enc}_{pk}(x)$
			\State Let $\tilde{C}$ to the circuit that takes $\tilde{x}$ as input to evaluate $\mathsf{Eval}_{evk}(C, \tilde{x})$
			\State The client delegates $\tilde{C}(\tilde{x})$ to the server using our $\QPIP_0$ protocol.
		\EndProcedure
	\end{algorithmic}
\end{algorithm}

\begin{thm}
	\autoref{ProtoPrivateDelegation} is IND-CPA secure.
\end{thm}
\begin{proof}
	This is... not so trivial.
\end{proof}

@@

>>>>

First we give a definition of CPA security for delegation schemes... TODO

\begin{dfn}
	A $\QPIP_\tau$ protocol is IND-CPA secure if, for any polynomial time prover $\cA$,
	$$\abs{\Pr[\cA]}$$
	where $x$ is the input of the verifier.
\end{dfn}

@@

\Ethan{TODO intro}

Here's what the client should do.

\begin{algorithm}
	\caption{Verifiable, secure, and constant round delegation}
	\label{ProtoPrivateDelegation}
	\begin{algorithmic}[1]
		\Procedure{Delegation}{C, x}
			\State Compute $\mathsf{QHE.Keygen}\rightarrow(pk, evk, sk)$
			\State Compute $\tilde{x}=\mathsf{Enc}_{pk}(x)$
			\State Let $\tilde{C}$ be the quantum circuit that takes $\tilde{x}$ as input to evaluate $\mathsf{Eval}_{evk}(C, \tilde{x})$
			\State Delegate $\tilde{C}(\tilde{x})$ to the server using our $\QPIP_0$ protocol.
			\State Get $y$ from the server
			\State \Return $\mathsf{QHE.Dec}(y)$
		\EndProcedure
	\end{algorithmic}
\end{algorithm}

@@

\begin{thm}
	\autoref{ProtoPrivateDelegation} is IND-CPA secure.
\end{thm}
\begin{proof}
	This is... not so trivial?
\end{proof}
